Supplementary materials for 'Openness and computational reproducibility in plant pathology: where we stand and a way forward

### 2023-01-05 analysis/paper/paper.Rmd
Supress the inclusion of figures in the documents for final submission

# Figures

```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the two categories evaluated, (A) displays 'Code availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable. (B) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", cache=FALSE, fig.env='figure'}

@@

```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualizations for each of six models fit to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals. The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and five-year impact factor of journal was tested for effect on code availability (E) and data availability (F). Scoring for 'Code Availability' was scored 1--3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable. And the scoring for 'Data Availability' was scored 1--3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper. Where 'yrep' indicate 50 random draws for model predictions and 'y' are the observed values. No article scored 3 for data availability. The fitness was found to be good for all models.", cache=FALSE, fig.env='figure'}

@@

```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the effect associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public. A test for equivalence was unable to detect any clear differences between *Phytopathology*&reg; and all other journals sharing computational materials (code). However, a test for equivalence found that articles in *Phytopathologia Mediterranea* were more likely to have data available than articles found in *Phytopathology*&reg;. Intervals in grey have a median value less than that of *Phytopathology*&reg;, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*&reg;. The region of practical equivalence (ROPE) is shown between two dotted lines. If the entire distribution falls within the ROPE, the hypothesis is accepted. If the entire distribution falls outside the ROPE, the hypothesis is rejected. In some cases, the data do not provide a definitive answer and the decision on H0 is undecided.', cache=FALSE, fig.env='figure'}
m_f1_eq <- equivalence_test(m_f1, rule = "bayes")
m_f2_eq <- equivalence_test(m_f2, rule = "bayes")

@@

```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the effect associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence was unable to detect an effect of year of publication on computational materials (code) being shared. A test for practical equivalence found that there was no effect of year of publication on the availability of supporting data. The region of practical equivalence (ROPE) is shown between two dotted lines. If the entire distribution falls within the ROPE, the hypothesis is accepted. If the entire distribution falls outside the ROPE, the hypothesis is rejected. In some cases, the data do not provide a definitive answer and the decision on H0 is undecided. Here, year is treated as a continuous variable to determine if there are changes over time in the likelihood of sharing code and data.', cache=FALSE, fig.env='figure'}

@@

```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence was undecided on any detectable effects of impact factor. The region of practical equivalence (ROPE) is shown between two dotted lines. If the entire distribution falls within the ROPE, the hypothesis is accepted. If the entire distribution falls outside the ROPE, the hypothesis is rejected. In some cases, the data do not provide a definitive answer and the decision on H0 is undecided. Here, impact factor is a continuous variable to determine if greater or lesser impact factor values affect the likelihood of sharing code and data.', cache=FALSE, fig.env='figure'}
m_h1_eq <- equivalence_test(m_h1, rule = "bayes")
m_h2_eq <- equivalence_test(m_h2, rule = "bayes")

@@

```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example of an open and reproducible research workflow. Starting with the question, determine the methodology, describe it, make it available and cite it. Data are used in analysis and any binary files or code are made available as supplements to the manuscript. Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time, and a DOI for final released products.', cache=FALSE, fig.env='figure'}

>>>>

# Figure Captions

```{r articleScores, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Aggregated article scores for each of the two categories evaluated, (A) displays 'Code availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable. (B) shows 'Data availability', where '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}

@@

```{r posteriors, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Posterior distribution visualizations for each of six models fit to scoring data that were used to evaluate factors on reproducibility of 450 papers published in 21 plant pathology journals or plant pathology focused articles from other specialized journals. The journal title was tested for an effect on code availability (A) and data availability (B), the year of publication was tested for an effect on code availability (C) and data availability (D), and five-year impact factor of journal was tested for effect on code availability (E) and data availability (F). Scoring for 'Code Availability' was scored 1--3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable. And the scoring for 'Data Availability' was scored 1--3 as follows, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper. Where 'yrep' indicate 50 random draws for model predictions and 'y' are the observed values. No article scored 3 for data availability. The fitness was found to be good for all models.", cache=FALSE, fig.env='figure', out.width=0, out.height=0}

@@

```{r journal-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the effect associated with the journal title for (A) computational materials (code) and (B) data being made readily available to the public. A test for equivalence was unable to detect any clear differences between *Phytopathology*&reg; and all other journals sharing computational materials (code). However, a test for equivalence found that articles in *Phytopathologia Mediterranea* were more likely to have data available than articles found in *Phytopathology*&reg;. Intervals in grey have a median value less than that of *Phytopathology*&reg;, the base level used for the analysis and articles in these journals could be less likely to share computational materials and data than articles published in *Phytopathology*&reg;. The region of practical equivalence (ROPE) is shown between two dotted lines. If the entire distribution falls within the ROPE, the hypothesis is accepted. If the entire distribution falls outside the ROPE, the hypothesis is rejected. In some cases, the data do not provide a definitive answer and the decision on H0 is undecided.', cache=FALSE, fig.env='figure', out.width=0, out.height=0}
m_f1_eq <- equivalence_test(m_f1, rule = "bayes")
m_f2_eq <- equivalence_test(m_f2, rule = "bayes")

@@

```{r year-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the effect associated with the year of publication for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence was unable to detect an effect of year of publication on computational materials (code) being shared. A test for practical equivalence found that there was no effect of year of publication on the availability of supporting data. The region of practical equivalence (ROPE) is shown between two dotted lines. If the entire distribution falls within the ROPE, the hypothesis is accepted. If the entire distribution falls outside the ROPE, the hypothesis is rejected. In some cases, the data do not provide a definitive answer and the decision on H0 is undecided. Here, year is treated as a continuous variable to determine if there are changes over time in the likelihood of sharing code and data.', cache=FALSE, fig.env='figure', out.width=0, out.height=0}

@@

```{r IF-parameters, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='Equivalence test for the affect associated with the publishing journal\'s five-year impact factor for (A) computational materials (code) and (B) data being made readily available to the public. A test for practical equivalence was undecided on any detectable effects of impact factor. The region of practical equivalence (ROPE) is shown between two dotted lines. If the entire distribution falls within the ROPE, the hypothesis is accepted. If the entire distribution falls outside the ROPE, the hypothesis is rejected. In some cases, the data do not provide a definitive answer and the decision on H0 is undecided. Here, impact factor is a continuous variable to determine if greater or lesser impact factor values affect the likelihood of sharing code and data.', cache=FALSE, fig.env='figure', out.width=0, out.height=0}
m_h1_eq <- equivalence_test(m_h1, rule = "bayes")
m_h2_eq <- equivalence_test(m_h2, rule = "bayes")

@@

```{r workflow-dia, echo=FALSE, message=FALSE, warning=FALSE, fig.cap='An example of an open and reproducible research workflow. Starting with the question, determine the methodology, describe it, make it available and cite it. Data are used in analysis and any binary files or code are made available as supplements to the manuscript. Source code and raw data are made available in a public repository, preferably with version control for tracking changes through time, and a DOI for final released products.', cache=FALSE, fig.env='figure', out.width=0, out.height=0}

### 2023-01-05 analysis/paper/supplementary_materials.Rmd
Supress the inclusion of figures in the documents for final submission

## Supplementary Figure

```{r evaluator-differences, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Criteria scores for 450 articles computational materials and data availability for each of the five evaluators. Each article was evaluated on a 0 to 3 scale for computational materials (Code) and raw data availability (Data) by one of five evaluators. Scoring for 'Code Availability' was scored 0-3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable. And the scoring for 'Data Availability' was scored 0-3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper."}
p <- import_notes() %>%
  mutate(
    comp_mthds_avail = as.numeric(as.character(comp_mthds_avail)),
    data_avail =  as.numeric(as.character(data_avail))
  ) %>%
  pivot_longer(cols = c("comp_mthds_avail",
                        "data_avail")) %>%
  ggplot(aes(y = as.factor(value), x = assignee)) +
  geom_count() +
  ylab("Criteria Score") +
  xlab("Evaluator") +
  ggtitle("Criteria scores by evaluator") +
  facet_wrap(name ~ .,
             labeller = labeller(name =
                                   c(
                                     "comp_mthds_avail" = "Code",
                                     "data_avail" = "Data"
                                   )))

>>>>

## Supplementary Figure Caption

```{r evaluator-differences, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Criteria scores for 450 articles computational materials and data availability for each of the five evaluators. Each article was evaluated on a 0 to 3 scale for computational materials (Code) and raw data availability (Data) by one of five evaluators. Scoring for 'Code Availability' was scored 0-3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no code was created to conduct the work that was detectable. And the scoring for 'Data Availability' was scored 0-3 where, '0' was 'Not available or not mentioned in the publication'; '1' was 'Available upon request to the author; '2' was 'Online, but inconvenient or non-permanent (e.g., login needed, paywall, FTP server, personal lab website that may disappear, or may have already disappeared)'; and '3' was 'Freely available online to anonymous users for foreseeable future (e.g., archived using Zenodo, dataverse or university library or some other proper archiving system)'; 'NA' indicates that no data were generated, e.g., a methods paper.", , out.width=0, out.height=0}
p <- import_notes() %>%
  mutate(
    comp_mthds_avail = as.numeric(as.character(comp_mthds_avail)),
    data_avail =  as.numeric(as.character(data_avail))
  ) %>%
  pivot_longer(cols = c("comp_mthds_avail",
                        "data_avail")) %>%
  ggplot(aes(y = as.factor(value), x = assignee)) +
  geom_count() +
  ylab("Criteria Score") +
  xlab("Evaluator") +
  ggtitle("Criteria scores by evaluator") +
  facet_wrap(name ~ .,
             labeller = labeller(name =
                                   c(
                                     "comp_mthds_avail" = "Code",
                                     "data_avail" = "Data"
                                   )))
